---
# title: "My Cheat Sheet for R Markdown Creation"
# author: "Joshua Soll"
output: html_document
# date: "2024-09-19"
bibliography: RMDCheatSheet.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# [***Header 1***]{.underline} {.tabset}

Adding a '\#' first in code creates the big header/header 1, and {.underline}{.tabset} in the code after the header lets you underline then create tabs for headers below

## ***Header 2 Tab 1***

### ***Header 3***

Create The above "Header 3" within a tab by using '\###', basically assigning a third level of header below the main and the header 2's, where tabs were created for the second header by putting the tabset code for header 1

```{r}
#Can make a code chunk using ```{r} and closing with ```

x <- 15
print(x)

#inputs and outputs will be shown
```

#### Creating a comment

You can also add comments that are unseen on the front end by highlighting text and typing command + shift + c

<!-- test comment here, should be unseen on the html front -->

## ***Header 2 Tab 2***

### Can do citations too. It is easiest to use the Visual Tab, click "insert" and then "citation", and select your citations.

[@baumgartner2011]

[@cauchy2023]

###Use Visual tab to insert most things
This includes any kind of graphics, and citations. It is easier than doing it in the source code.

